R Notebook

### 2018-03-31 analysis/final_analysis.Rmd
Import subject info; implement exclusions

@@

@@

```{r}
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)

d_raw <- read_tsv('../data/final/experiment2/planned_sample/chatMessage/message.csv') %>%
  filter(iterationName == 'planned_sample') %>%
  filter(role == 'speaker')

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d_raw %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)

# Some speakers relied purely on location in grid
pureLocation <- c('0180-a541e54c-5dea-4d06-9a21-9b842316eb59', '0101-0b659560-f05a-471a-89ac-60469e9c867f')
badGames <- c(incompleteIDs, pureLocation)

@@

```{r}
basic.d <- d %>%
  filter(hidden == 'no') %>%
  group_by(gameid, context) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(context, m) %>%
  mutate(diff = close - far)

@@

```{r}
hidden.d <- d %>%
  group_by(gameid, context, hidden) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(hidden, m) %>%
  mutate(diff = yes - no)

@@

```{r}
ggplot(hidden.d %>% group_by(context) %>% mutate(m = mean(diff)), aes(x = diff)) +
    geom_histogram(binwidth = 0.33) +
    theme_bw() +
    geom_vline(xintercept = 0, linetype = 2) +
    geom_vline(aes(xintercept = m), color = 'red') +
    facet_wrap(~ context) +
    # ylim(1,12) +
    xlim(-5,5) +
    theme(aspect.ratio = 1)
```

@@

>>>>

# General imports

```{r}
library(jsonlite)
library(tidyverse)
library(ggthemes)
library(lme4)
library(lmerTest)
```

@@

## Import turk survey data

```{r}
path <- "../data/final/experiment2/planned_sample/turk/"
files = dir(path, pattern = "*.json")

subjInfo = data.frame()

for (f in files) {
  jf = paste0(path, f)
  jd = read_json(jf)

  newRow = data.frame()
  if(!is.null(jd$answers$subject_information)) {
    # for(property in names(jd$answers$subject_information) {
    #   if(!is.null(jd$answers$subject_information[property])) {
    #     newRow[property] = jd$answers$subject_information[property]
    #   } else 
    #     newRow[property] = NA
    # }
    newRow = data.frame(gameid = jd$answers$subject_information$gameID,
                        role = jd$answers$subject_information$role,
                        gameLength = jd$answers$subject_information$totalLength,
                        thinksHuman = ifelse(!is.null(jd$answers$subject_information$thinksHuman), jd$answers$subject_information$thinksHuman, NA),
                        understandsInstructions = jd$answers$subject_information$confused,
                        nativeEnglish = jd$answers$subject_information$nativeEnglish,
                        ratePartner = jd$answers$subject_information$ratePartner,
                        comments = jd$answers$subject_information$comments,
                        strategy = jd$answers$subject_information$strategy)
    subjInfo = bind_rows(subjInfo, newRow)
  }
}

@@

```{r}
d_raw <- read_tsv('../data/final/experiment2/planned_sample/chatMessage/message.csv') %>%
  filter(iterationName == 'planned_sample') %>%
  filter(role == 'speaker')

# nonNativeSpeakerIDs <- unique((tangramSubjInfo %>% filter(nativeEnglish != "yes"))$gameid)
incompleteIDs <- unique((d_raw %>% group_by(gameid) %>% 
                           filter(length(unique(trialNum)) != 24))$gameid)
confused <- unique((subjInfo %>% filter(understandsInstructions != 'yes'))$gameid)

# Some speakers relied on location in grid
location_abusers <- c('8219-bb7861c1-43f4-480c-906b-8441c583c0ab', '7726-3d4a266f-e56d-4afb-9a79-b40deb690a76', '5684-f09de856-4d64-423c-b342-b30e7325eb0e', '7600-346d56b5-bd76-406f-befb-6b47e07d5916')
badGames <- c(incompleteIDs, pureLocation, confused)

@@

```{r}
basic.d <- d %>%
  filter(hidden == 'no') %>%
  group_by(gameid, context) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(context, m) %>%
  mutate(diff = close- far,
         ratio = close / far)

@@

```{r}
hidden.d <- d %>%
  group_by(gameid, context, hidden) %>%
  summarize(m = mean(numRawWords)) %>%
  spread(hidden, m) %>%
  mutate(diff = yes- no)

@@

```{r}
ggplot(hidden.d %>% group_by(context) %>% mutate(m = mean(diff)), aes(x = diff)) +
    geom_histogram(binwidth = 0.33) +
    theme_bw() +
    geom_vline(xintercept = 0, linetype = 2) +
    geom_vline(aes(xintercept = m), color = 'red') +
    facet_wrap(~ context) +
    # ylim(1,12) +
    xlim(-6,6) +
    theme(aspect.ratio = 1)

ggsave("~/Downloads/histograms.pdf")
```

@@

Clusters

```{r}
hidden.d %>% 
  filter(context == 'far') %>% 
  mutate(group = case_when(diff < -0 ~ 'anti',
                           diff > 0 ~ 'pro',
                           TRUE ~ 'all_the_things')) %>%
  group_by(group) %>% tally()
```
